% used template from moderncv
\documentclass[11pt,a4paper]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{grey}

\usepackage[utf8]{inputenc}
\usepackage{footmisc}

\usepackage[vscale=0.9, hscale=0.8]{geometry}

\name{Yury}{Usishchev}
\address{Moscow, Russia}
\phone[mobile]{+7~916~920~79~91}
\email{jolfzverb@gmail.com}
\social[linkedin]{usishchev}
\social[github]{jolfzverb}
%\photo[64pt][0.4pt]{picture} %TODO
\pretolerance=10000
\tolerance=-1

\begin{document}

\makecvtitle
\section{Summary}
\cvline
  {}{
Three years of experience in toolchain-related development including
contribution to open-source projects like binutils, coreutils, EFL.
Deep knowledge of system libraries (glibc, rtld) and toolchain parts (GCC, binutils, LLVM).
Lots of experience in debugging and single-line text processing.
}

\section{Technical skills}
\label{sec:skills}
\subsection{Basic skills}
\cvline
  {Languages}{C, C++, bash, perl, python, sed}
\cvline
  {Hardware}{ARMv7, ARMv8, NEON instructions}
\cvline
  {English}{Upper intermediate}
\subsection{Developer tools}
\cvdoubleitem
  {SCM}{git, svn}
  {Testing}{googletest, check; ctest, dejagnu}
\cvdoubleitem
  {Build}{make, cmake, autotools}
  {Packaging}{rpm, rpmbuild}
\cvdoubleitem
  {Debug}{gdb, strace, objdump, readelf}
  {Status}{top, iotop, traceroute, tcpdump}
\cvdoubleitem
  {Profiling}{valgrind, perf}
  {Docs}{doxygen, \LaTeX}
\cvdoubleitem
  {Bug tracking}{Gerrit, Jira, Confluence}
  {Build system}{OBS}

\section{Experience}
\label{sec:exp}
\cventry {2016--now} {Software Engineer} {Samsung Research Russia} {Moscow} {}
        {Tizen toolchain support and development, Tizen Toolchain team.\newline{}
          \textbf{Project details:}\newline{}
          Support and improvement of Tizen platform through toolchain technologies. This includes keeping toolchain sources up-to-date, system-wide optimizations and sanitization (LTO, PGO, Sanitizers).\newline{}
          \textbf{Responsibilities:}
          \begin{itemize}
          \item Develop a tool set capable of automatic reduce of symbol visibility of C and C++ packages.
          \end{itemize}
\textbf{Personal deliverables and artifacts:}
\begin{itemize}
\item Created tool set:
\begin{itemize}
\item Clang LibTooling based tool for source processing (C++)
\item Bash script to process OBS- and git-related aspect of package processing.
  \end{itemize}
\item Several patches with cleanup and visibility reduce were promoted to upstream.
  \end{itemize}
        }
\cventry {2015--2016} {Software Engineer} {Samsung Research Russia} {Moscow} {}
        {Tizen toolchain support and development, Tizen Toolchain team.\newline{}
          \textbf{Project details:}\newline{}
          Support and improvement of Tizen platform through toolchain technologies. This included keeping toolchain sources up-to-date, system-wide optimizations and sanitization(LTO, Address Sanitizer),
          AArch64-specific optimizations of core libraries and toolchain packages.
          \textbf{Responsibilities:}
          \begin{itemize}
          \item Support of development projects in Tizen OBS
          \item Enabling of Address Sanitizer for Tizen packages
          \item Porting of evas optimization to AArch64
          \end{itemize}
\textbf{Personal deliverables and artifacts:}
\begin{itemize}
\item Reimplemented hot paths in evas library of Enlightenment Foundation Libraries using GCC intrinsics. Performance improvements up to 30\% for AArch64.
\item Enabled project-wide address sanitizer, found and fixed several bugs in Tizen and upstream codebase(coreutils and binutils)
\item Enabled project-wide clang build
\item Refactored build acceleration system for ARMv7 and ARMv8 builds in Tizen OBS
  \end{itemize}
        }

\cventry{2014--2015}{Junior Software Engineer}{Samsung Research Russia}{Moscow}{}
        {Tizen AArch64 enabling, Tizen Toolchain team.\newline{}
\textbf{Project details:}\newline{}
Enable AArch64 build for all Tizen packages in main Tizen OBS instance. This included manual bootstrap of core packages, required for automated builds in OBS environment,
project configuration and fix of all build problems. Toolchain packages were updated as well for better support of AArch64.\newline{}
\textbf{Responsibilities:}
\begin{itemize}
\item Manual build of rpm packages for later use in OBS
\item Project acquaintance (configuration consistency, packages build fix)
\end{itemize}
\textbf{Personal deliverables and artifacts:}
\begin{itemize}
\item Learned OBS and RPM internals
\item AArch64 was enabled for all Tizen profiles
\item Lots of patches and build fixes were introduced to Tizen codebase
\end{itemize}}

\cventry{2013--2014}{Junior Software Engineer}{Samsung Research Russia}{Moscow}{}
        {Optimizing Tizen platform, Tizen Toolchain team.\newline{}
\textbf{Project details:}\newline{}
Optimization of Tizen operating system for mobile devices (ARMv7). Profiling and optimization of Tizen applications (both C and C++) startup and operation performance,
binary size, battery consumption from point of view of compiler technologies. Deliverables included lots of system-wide optimization by compiler options (visibility=hidden, autovectorization, PGO)
and several hand-written optimizations of core libraries and software.\newline{}
\textbf{Responsibilities:}
\begin{itemize}
\item Performance, battery consumption profiling
\item Applications and library optimization
\end{itemize}
\textbf{Personal deliverables and artifacts:}
\begin{itemize}
\item Learned arm SIMD instruction set - NEON
\item Optimized hot paths in evas library of Enlightenment Foundation Libraries using inline vector assembly. Performance improvements - up to 30\% on library benchmarks on ARMv7.
\end{itemize}}

\cventry{2012--2014}{Junior Researcher}
        {Technological Institute for Superhard and Novel Carbon Materials}
        {Moscow}{}{Development of new image processing system in
                   Scanning Probe Microscope(C++, OpenCV)}


\section{Education}
\label{sec:edu}
\cventry{2012--2014}{Applied Mathematics and Physics, Master}
        {Moscow Institute of Physics and Technology}{}{}{}
\cventry{2007--2012}{Applied Mathematics and Physics, Bachelor}
        {Moscow Institute of Physics and Technology}{}{}{}


\end{document}
